\textsc{Atomic modeling of argon}\\ \footnotesize{\textsc{Project 5 --- FYS3150}}

### 2015-12-07 projects/project_5/molecular_dynamics/article/article.tex
done?

\begin{abstract}
    In this project we explore the world of molecular dynamics. We are first
    presented with the skeleton of a working MD-program, and we are asked to
    implement the functionality we need as we go along. We look at the time
    evolution of a system of argon, with an initial face-centered cubic lattice
    configuration. The atoms are under the influence of the Lennard-Jones
    potential. We use the Velocity-Verlet as our time integrator of choice, and
    we compare this to the Euler-Cromer method in terms of energy conservation
    properties. We also compute the melting temperature of argon, by means of
    the Einstein relation and diffusion constant.
\end{abstract}
\doublespacing
\tableofcontents
\listoffigures      
\singlespacing

\section{Introduction}
\label{sec:introduction}

@@

>>>>

\begin{abstract}
    In this project we explore the world of molecular dynamics. We are first
    presented with the skeleton of a working MD-program, and we are asked to
    implement the functionality we need as we go along. We look at the time
    evolution of a system of argon, with an initial face-centered cubic lattice
    configuration. The atoms are under the influence of the Lennard-Jones
    potential. We use the Velocity-Verlet as our time integrator of choice, and
    we compare this to the Euler-Cromer method in terms of energy conservation
    properties. We also compute the melting temperature of argon, by means of
    the Einstein relation and diffusion constant.
\end{abstract}
\clearpage
\doublespacing
\tableofcontents
\listoffigures      
\singlespacing
\clearpage
\section{Introduction}
\label{sec:introduction}

@@

In this project we have mainly been concerned with the properties of argon. We
have most notably looked at how a molecular dynamics simulation of argon using
the Lennard-Jones potential behaves.  The results tells us that the
experimental values for argon are not properly reflected in the simulations,
however the system does more or less behave as it should, albeit for a larger
temperature. When considering the force model we made some optimizations to the
potential, and only looked at the interactions between atoms sufficiently close
to each other. This lead to a significant increase in simulation speed, from a
time complexity of $\mathcal{O}(N^2)$ to one of $\mathcal{O}(N)$.

We also chose to implement the Velocity Verlet algorithm as our time
integrator, in preference over the more basic Euler-Cromer method. This lead to
a more stable energy conservation over varying time steps. The improvement was
from approximately linear to a constant.

We also considered the melting temperature of argon, and measured it to be
somewhere close to $300K$, which does not really coincide with the
experimentally observed melting temperature of approximately $84K$. Despite
this disparity the system at least behaves consistent.
